\Large\bf Scalable and Probabilistic Leaderless BFT Consensus through Metastability

### 2020-11-07 paper_fr.tex
S5 - titre de schéma etc.

%The Snow family is presented in the form of single-decree, binary consensus for its own theoretical value and simplicity.
%On the other hand, we show later in Section~\ref{sec:implementation} our practical payment system, Avalanche, utilizes multiple Snowball instances to support standard Bitcoin-like transactions. %, by humbly cheating in two ways.
%First, instead of a single replicated state machine (RSM) model, where the system determines a sequence of totally-ordered transactions $T_0, T_1, T_2, \ldots$ issued by any client, we adopt a \emph{parallel consensus model}, where each client interacts independently with its own RSMs and optionally transfers ownership of its RSM to another client. The system establishes only a partial order between dependent transactions.
%Second,
%O In a cryptocurrency setting, cryptographic signatures enforce that only a key owner is able to create a transaction that spends a particular coin. Since correct clients follow the protocol as prescribed and never double spend coins, in Avalanche, they are guaranteed both safety and liveness for their \emph{virtuous} transactions. In contrast, liveness is not guaranteed for \emph{rogue} transactions, submitted by Byzantine clients, which conflict with one another. Such decisions may stall in the network, but have no safety impact on virtuous transactions.
Dans une configuration de cryptomonnaie, les signatures cryptographiques imposent que seul le possesseur de la clef soit capable de créer une transaction dépensant un dépôt donné. Comme les clients corrects suivent le protocole tel qu'il est prescrit et ne peuvent pratiquer la double dépense, ils ont la garantie tant de sûreté de fonctionnement que de vitalité pour leurs transactions \emph{vertueuses}. Par contraste, la vitalité n'est pas garantie pour les transactions \emph{malveillantes} soumises par des clients byzantins, qui entrent mutuellement en conflit. Ces décisions peuvent arrêter le réseau mais n'ont pas d'impact sur les transactions vertueuses.
%O We show that this is a sensible tradeoff, and that the resulting system is sufficient for building complex payment systems.
Nous montrons que ce compromis est sensé et que le système qui en résulte suffit à bâtir des systèmes de paiement complexes.

>>>>

%The Snow family is presented in the form of single-decree, binary consensus for its own theoretical value and simplicity.
%On the other hand, we show later in Section~\ref{sec:implementation} our practical payment system, Avalanche, utilizes multiple Snowball instances to support standard Bitcoin-like transactions. %, by humbly cheating in two ways.
%First, instead of a single replicated state machine (RSM) model, where the system determines a sequence of totally-ordered transactions $T_0, T_1, T_2, \ldots$ issued by any client, we adopt a \emph{parallel consensus model}, where each client interacts independently with its own RSMs and optionally transfers ownership of its RSM to another client. The system establishes only a partial order between dependent transactions.
%Second,
%O In a cryptocurrency setting, cryptographic signatures enforce that only a key owner is able to create a transaction that spends a particular coin. Since correct clients follow the protocol as prescribed and never double spend coins, in Avalanche, they are guaranteed both safety and liveness for their \emph{virtuous} transactions. In contrast, liveness is not guaranteed for \emph{rogue} transactions, submitted by Byzantine clients, which conflict with one another. Such decisions may stall in the network, but have no safety impact on virtuous transactions.
Dans une configuration de cryptomonnaie, les signatures cryptographiques imposent que seul le possesseur de la clef soit capable de créer une transaction dépensant un dépôt donné. Comme les clients corrects suivent le protocole tel qu'il est prescrit et ne peuvent pratiquer la double dépense, ils ont la garantie tant de sûreté de fonctionnement que de vitalité pour leurs transactions \emph{vertueuses}. Par contraste, la vitalité n'est pas garantie pour les transactions \emph{malveillantes} soumises par des clients byzantins, lesquelles entrent mutuellement en conflit. Ces décisions peuvent arrêter le réseau mais n'ont pas d'impact sur les transactions vertueuses.
%O We show that this is a sensible tradeoff, and that the resulting system is sufficient for building complex payment systems.
Nous montrons que ce compromis est sensé et que le système qui en résulte suffit à bâtir des systèmes de paiement complexes.
